Filter check

### 2019-01-16 R/filter-check.Rmd
Reduce length requirement for long pacbio quality trimming (because these will now be applied to ITSx products)

if (interactive()) {
  base.dir <- getwd() %>%
    str_extract(".*oueme-fungi-transect")
  data.dir <- file.path(base.dir, "data")
  lab.dir <- file.path(data.dir, "lab_setup")
  seq.dir <- file.path(base.dir, "raw_data")
  dataset.file <- file.path(lab.dir, "datasets.csv")
  datasets <- read_csv(dataset.file)

  reads <- datasets %>%
    mutate(demux.dir = file.path(seq.dir, Dataset, Seq.Run, "demultiplex"),
           files = map(demux.dir, list.files, pattern = "*.fastq.gz",
                       full.names = TRUE)) %>%
    unnest() %>%
    mutate(filesize = file.size(files)) %>%
    filter(filesize > 0) %>%
    mutate(fastq = map(files, readFastq),
           eexp = map(fastq, ~ 10^(-1 * as(.@quality, "matrix")/10) %>%
                        rowSums(na.rm = TRUE)),
           length = map(fastq, width)) %>%
    select(-fastq) %>%
    unnest %>%
    mutate(erate = eexp/length)
}
```

@@

```
```{r}
counts <- read_csv(file.path(data.dir, "fastq.counts"), col_names = c("file", "reads"))
counts %<>% mutate(dataset = map(file, str_extract, datasets$Dataset) %>%
                     map_chr(purrr::compose(dplyr::first, sort, unique)),
                   seq.run = map(file, str_extract, datasets$Seq.Run) %>%
                     map_chr(purrr::compose(dplyr::first, sort, unique)),
                   well = str_extract(file, "[A-H]\\d\\d?"),
                   shard = str_extract(file, "\\bx[a-z][a-z]\\b"),
                   is.shard = !is.na(shard),
                   region = str_extract(file, "(ITS[12]|LSU)"),
                   is.trim = str_detect(file, "trim"),
                   is.demux = is.na(region) & !is.trim & !is.na(well),
                   type = ifelse(is.trim, "trim",
                                 ifelse(!is.na(region), "ITSx",
                                        ifelse(is.demux, "demux",
                                               "original"))),
                   plate = str_extract(file, "00\\d")) %>%
  group_by(dataset, type, region, is.shard) %>%
  summarize(reads = sum(reads)) %>%
  ungroup() %>%
  select(-is.shard) %>%
  unique() %>%
  spread(key = "type", value = "reads") %>%
  select(dataset, original, demux, region, ITSx, trim) %>%
  filter(!is.na(dataset))

@@

short.pacbio <- new.env()
load(file.path(data.dir, "short-pacbio_pb_483.asv.Rdata"), envir = short.pacbio)
remove("derep", envir = short.pacbio)
assign("seq.tab", dada2::makeSequenceTable(short.pacbio$asv), envir = short.pacbio)

@@

dadacounts <- tribble( ~ dataset, ~region, ~assigned, ~asv,
                       "short-pacbio", NA, sum(short.pacbio$seq.tab), ncol(short.pacbio$seq.tab),
                       "long-pacbio", "ITS1", sum(long.pacbio.ITS1$seq.tab), ncol(long.pacbio.ITS1$seq.tab),
                       "long-pacbio", "ITS2", sum(long.pacbio.ITS2$seq.tab), ncol(long.pacbio.ITS2$seq.tab),
                       "long-pacbio", "LSU", sum(long.pacbio.LSU$seq.tab), ncol(long.pacbio.LSU$seq.tab),
                       "short-ion", NA, sum(short.ion$seq.tab), ncol(short.ion$seq.tab))
```

>>>>

#if (interactive()) {
  base.dir <- getwd() %>%
    str_extract(".*oueme-fungi-transect")
  data.dir <- file.path(base.dir, "data")
  lab.dir <- file.path(data.dir, "lab_setup")
  seq.dir <- file.path(base.dir, "raw_data")
  dataset.file <- file.path(lab.dir, "datasets.csv")
  datasets <- read_csv(dataset.file)

  reads <- datasets %>%
    mutate(demux.dir = file.path(seq.dir, Dataset, Seq.Run, "demultiplex"),
           files = map(demux.dir, list.files, pattern = "*.fastq.gz",
                       full.names = TRUE)) %>%
    unnest() %>%
    mutate(filesize = file.size(files)) %>%
    filter(filesize > 0) %>%
    mutate(fastq = map(files, readFastq),
           eexp = map(fastq, ~ 10^(-1 * as(.@quality, "matrix")/10) %>%
                        rowSums(na.rm = TRUE)),
           length = map(fastq, width)) %>%
    select(-fastq) %>%
    unnest %>%
    mutate(erate = eexp/length)
#}
```

@@

```
```{r}
counts <- read_csv(file.path(data.dir, "fastq.counts"), col_names = c("file", "reads"))
counts %<>% mutate(dataset = map(file, str_extract, datasets$Dataset) %>%
                     map_chr(purrr::compose(dplyr::first, sort, unique)),
                   seq.run = map(file, str_extract, datasets$Seq.Run) %>%
                     map_chr(purrr::compose(dplyr::first, sort, unique)),
                   well = str_extract(file, "[A-H]\\d\\d?"),
                   shard = str_extract(file, "\\bx[a-z][a-z]\\b"),
                   is.shard = !is.na(shard),
                   region = str_extract(file, "(ITS[12]|LSU)"),
                   is.trim = str_detect(file, "trim"),
                   is.demux = is.na(region) & !is.trim & !is.na(well),
                   type = ifelse(is.trim, "trim",
                                 ifelse(!is.na(region), "ITSx",
                                        ifelse(is.demux, "demux",
                                               "original"))),
                   plate = str_extract(file, "00\\d")) %>%
  group_by(dataset, type, region, is.shard) %>%
  summarize(reads = sum(reads)) %>%
  ungroup() %>%
  select(-is.shard) %>%
  unique() %>%
  spread(key = "type", value = "reads") %>%
  select(dataset, original, demux, region, ITSx, trim) %>%
  filter(!is.na(dataset)) %>%
  group_by(dataset) %>%
  mutate(original = na.omit(original),
         demux = na.omit(demux)) %>%
  filter(all(is.na(region)) | !is.na(region))

@@

d
short.pacbio <- new.env()
load(file.path(data.dir, "short-pacbio_pb_483.asv.Rdata"), envir = short.pacbio)
remove("derep", envir = short.pacbio)
assign("seq.tab", dada2::makeSequenceTable(short.pacbio$asv), envir = short.pacbio)

@@

dadacounts <- tribble( ~ dataset, ~region, ~assigned, ~asv,
                       "short-pacbio", NA, sum(short.pacbio$seq.tab), ncol(short.pacbio$seq.tab),
                       "long-pacbio", "ITS1", sum(long.pacbio.ITS1$seq.tab), ncol(long.pacbio.ITS1$seq.tab),
                       "long-pacbio", "ITS2", sum(long.pacbio.ITS2$seq.tab), ncol(long.pacbio.ITS2$seq.tab),
                       "long-pacbio", "LSU", sum(long.pacbio.LSU$seq.tab), ncol(long.pacbio.LSU$seq.tab),
                       "short-ion", NA, sum(short.ion$seq.tab), ncol(short.ion$seq.tab))

demux.counts %>% left_join(dadacounts) %>%
  filter(!is.na(assigned))
```
